Beam-Helicity and Beam-Charge Asymmetries \\ in the \red{DVCS and Bethe--Heitler processes} on \\ an Unpolarised Proton Target \underline{Paper Tag: PDVCS0607 (v2.3)} \underline{Drafting Committee: DC90 (\today)}

### 2012-01-20 theory.tex
Version 2.3

The four-fold differential cross section for the exclusive leptoproduction of real photons
from an unpolarised \red{hydrogen} target can be written as \cite{Bel02b}
\begin{center}
\begin{equation}
\frac{\textrm{d}^4\sigma}{\textrm{d}x_{\textrm{B}}\textrm{d}Q^{2}\textrm{d}
|t|\textrm{d}\phi} =
\frac{x_{\textrm{B}}e^{6}}{32(2\pi)^{4} Q^{4}\sqrt{1+\epsilon^{2}}}
|\tau|^{2},
\end{equation}
\end{center}
where $e$ is the elementary
charge, $\epsilon=2x_\textrm{B}\frac{M}{Q}$ with $M$
the target mass, and $\phi$ is the
azimuthal angle between the scattering and production planes \cite{Tre04}.
The {square of the} scattering amplitude $|\tau|^2$ can be written as
\begin{center}
\begin{equation}
|\tau|^{2} = |\tau_{\textrm{BH}}|^{2} +
|\tau_{\textrm{DVCS}}|^{2} + \textrm{I},
\end{equation}
\end{center}
with contributions from the \textrm{BH} process ($\tau_{\textrm{\textrm{BH}}}$),
the DVCS process
($\tau_{\textrm{DVCS}}$) and their interference term (I). These
contributions can be written as
\begin{eqnarray}
 |\tau_{\textrm{BH}}|^{2} &=&
 \frac{K_{\textrm{BH}}}{\mathcal{P}_{1}(\phi)\mathcal{P}_{2}(\phi)} \left(c_{0,\textrm{unp}}^{\textrm{BH}} + \sum_{n=1}^2
  c_{\textrm{unp},n}^{\textrm{BH}}\cos(n\phi)\right), \label{e:tbh}\\
|\tau_{\textrm{DVCS}}|^{2} &=&
K_{\textrm{DVCS}}\left(c_{0,\textrm{unp}}^{\textrm{DVCS}} +
\sum_{n=1}^2
c_{\textrm{unp},n}^{\textrm{DVCS}}\cos(n\phi) + \lambda\,
s_{1,\textrm{unp}}^{\textrm{DVCS}}\sin\phi\right)\,\textrm{and}
\label{e:tdvcs}\\
 \textrm{I} &=& \frac{- e_\ell
K_{\textrm{I}}}{\mathcal{P}_{1}(\phi)\mathcal{P}_{2}(\phi)}\left(c_{0,\textrm{unp}}^{\textrm{
I}}+
\sum_{n=1}^3 c_{\textrm{unp},n}^{\textrm{I}}\cos(n\phi) + \lambda \sum_{n=1}^2
s_{\textrm{unp},n}^{\textrm{I}}\sin(n\phi)\right),\label{e:ti}
\end{eqnarray}
where $\mathcal{P}_1(\phi)$ and $\mathcal{P}_2(\phi)$ are the lepton propagators
of the BH process, $\lambda$ is the
helicity of the lepton beam and $e_\ell$ is the \red{sign of the} charge of
 the \red{beam} lepton.  The
quantities $K_{\textrm{BH}}=1/(x_\textrm{B}^2t(1+\epsilon^2)^2)$,
$K_{\textrm{DVCS}}=1/Q^2$
and $K_{\textrm{I}}=1/(x_{\textrm{B}}yt)$ are kinematic factors, where
$y$ is the fraction of the beam energy carried by the virtual photon in
the target rest frame. A full explanation of the Fourier coefficients [$c_{\textrm{unp},n}^V,s_{\textrm{unp},n}^W$]\red{, where V (W) denotes BH, DVCS or I (DVCS or I),} can be found in ref.~\cite{Bel02b}.

@@

The Fourier coefficients that receive leading-twist contributions are $c_{0,\textrm{unp}}^{\textrm{I}}$, \red{$c_{1,\textrm{unp}}^{\textrm{I}}$ and $s_{1,\textrm{unp}}^{\textrm{I}}$}. All of these Fourier coefficients have a dominant contribution from the $\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$-function:
\begin{eqnarray}
c_{0,\textrm{unp}}^{\textrm{I}} &\approx&-8(2-y)\frac{(2-y^2)}{(1-y)}K^2\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}\label{eq:c0}
\\
c_{1,\textrm{unp}}^{\textrm{I}} &\approx&\,8K(2- 2y + y^{2})\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}\,,\label{eq:c1}
\\
s_{1,\textrm{unp}}^{\textrm{I}} &\approx&\,8Ky(2-y)\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}\quad\,. \label{eq:s1}
\end{eqnarray}
The definition of the kinematic factor $K$ is~\cite{Bel02b}\red{:}
\begin{equation}
K^2=\frac{t}{Q^2}\Big(1-\frac{t_{\textrm{min}}}{t}\Big)\Big(1-x_{\textrm{B}}\Big)\Big(1-y-\frac{y^2\epsilon^2}{4}\Big)\Big\lbrace\sqrt{1+\epsilon^2}+\frac{4x_{\textrm{B}}(1-x_{\textrm{B}})+\epsilon^2}{4(1-x_{\textrm{B}})}
\frac{t_{\textrm{min}}-t}{Q^2}\Big\rbrace\red{\,.}\label{eq:K}
\end{equation} 
The factor of $\Big(1-\frac{t_{\textrm{min}}}{t}\Big)$ implies that amplitudes proportional to these fourier coefficients vanish as $-t$ approaches its minimum value.
The $\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$-function can be
written
\cite{Bel02b} 
\begin{equation}
 \mathcal{C}_{\textrm{unp}}^{\textrm{I}} = F_{1}\mathcal{H} + \frac{x_{\textrm{B}}}{2-x_{\textrm{B}}}(F_{1}+F_{2})\widetilde{\mathcal{H}} -\frac{t}{4M^{2}}F_{2}\mathcal{E},
\label{Eq_cunp}
\end{equation}
where $F_{1}$ and $F_{2}$ are respectively the Dirac and Pauli form
factors of the nucleon and $\mathcal{H}$, $\widetilde{\mathcal{H}}$ and
$\mathcal{E}$ are CFFs that relate respectively to the GPDs $H$,
$\widetilde{H}$ and $E$.  In H{\sc ermes} kinematic
conditions (where $x_{\textrm{B}}$ and $\frac{-t}{4M^2}$ are of order 0.1), the
contributions of CFFs $\widetilde{\mathcal{H}}$ and $\mathcal{E}$ can be
neglected in eq.~\ref{Eq_cunp} with respect to $\mathcal{H}$ (in first approximation) since they
are kinematically suppressed by an order of magnitude or more.
Hence, the behaviour of
$\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ is determined by CFF $\mathcal{H}$
and therefore GPD $H$ can be constrained through
measurements of the $\sin\phi$ and $\cos\phi$ terms of the $\mathcal{A}^{\textrm{I}}_{\textrm{LU}}(\phi)$ and $\mathcal{A}_{\textrm{C}}(\phi)$ asymmetries respectively.

>>>>

The four-fold differential cross section for the exclusive leptoproduction of real photons
from an unpolarised \red{hydrogen} target can be written as \cite{Bel02b}
\begin{center}
\begin{equation}
\frac{\textrm{d}^4\sigma}{\textrm{d}x_{\textrm{B}}\textrm{d}Q^{2}\textrm{d}
|t|\textrm{d}\phi} =
\frac{x_{\textrm{B}}e^{6}}{32(2\pi)^{4} Q^{4}\sqrt{1+\epsilon^{2}}}
|\tau|^{2},
\end{equation}
\end{center}
where $e$ is the elementary
charge, $\epsilon=2x_\textrm{B}\frac{M}{Q}$ with $M$
the target mass, and $\phi$ is the
azimuthal angle between the scattering and production planes \cite{Tre04}.
The {square of the} scattering amplitude $|\tau|^2$ can be written as
\begin{center}
\begin{equation}
|\tau|^{2} = |\tau_{\textrm{BH}}|^{2} +
|\tau_{\textrm{DVCS}}|^{2} + \textrm{I},
\end{equation}
\end{center}
with contributions from the \textrm{BH} process ($\tau_{\textrm{\textrm{BH}}}$),
the DVCS process
($\tau_{\textrm{DVCS}}$) and their interference term (I). These
contributions can be written as
\begin{eqnarray}
 |\tau_{\textrm{BH}}|^{2} &=&
 \frac{K_{\textrm{BH}}}{\mathcal{P}_{1}(\phi)\mathcal{P}_{2}(\phi)} \left(c_{\textrm{unp},0}^{\textrm{BH}} + \sum_{n=1}^2
  c_{\textrm{unp},n}^{\textrm{BH}}\cos(n\phi)\right), \label{e:tbh}\\
|\tau_{\textrm{DVCS}}|^{2} &=&
K_{\textrm{DVCS}}\left(c_{\textrm{unp},0}^{\textrm{DVCS}} +
\sum_{n=1}^2
c_{\textrm{unp},n}^{\textrm{DVCS}}\cos(n\phi) + \lambda\,
s_{\textrm{unp},1}^{\textrm{DVCS}}\sin\phi\right)\,\textrm{and}
\label{e:tdvcs}\\
 \textrm{I} &=& \frac{- e_\ell
K_{\textrm{I}}}{\mathcal{P}_{1}(\phi)\mathcal{P}_{2}(\phi)}\left(c_{\textrm{unp},0}^{\textrm{
I}}+
\sum_{n=1}^3 c_{\textrm{unp},n}^{\textrm{I}}\cos(n\phi) + \lambda \sum_{n=1}^2
s_{\textrm{unp},n}^{\textrm{I}}\sin(n\phi)\right),\label{e:ti}
\end{eqnarray}
where $\mathcal{P}_1(\phi)$ and $\mathcal{P}_2(\phi)$ are the lepton propagators
of the BH process, $\lambda$ is the
helicity of the lepton beam and $e_\ell$ is the \red{sign of the} charge of
 the \red{beam} lepton.  The
quantities $K_{\textrm{BH}}=1/(x_\textrm{B}^2t(1+\epsilon^2)^2)$,
$K_{\textrm{DVCS}}=1/Q^2$
and $K_{\textrm{I}}=1/(x_{\textrm{B}}yt)$ are kinematic factors, where
$y$ is the fraction of the beam energy carried by the virtual photon in
the target rest frame. A full explanation of the Fourier coefficients [$c_{\textrm{unp},n}^V,s_{\textrm{unp},n}^W$]\red{, where V (W) denotes BH, DVCS or I (DVCS or I),} can be found in ref.~\cite{Bel02b}.

@@

The Fourier coefficients that receive leading-twist contributions are $c_{\textrm{unp},0}^{\textrm{I}}$, \red{$c_{\textrm{unp},1}^{\textrm{I}}$ and $s_{\textrm{unp},1}^{\textrm{I}}$}. All of these Fourier coefficients have a dominant contribution from the $\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$-function:
\begin{eqnarray}
c_{\textrm{unp},0}^{\textrm{I}} &\approx&-8(2-y)\frac{(2-y^2)}{(1-y)}K^2\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}\label{eq:c0}
\\
c_{\textrm{unp},1}^{\textrm{I}} &\approx&\,8K(2- 2y + y^{2})\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}\,,\label{eq:c1}
\\
s_{\textrm{unp},1}^{\textrm{I}} &\approx&\,8Ky(2-y)\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}\quad\,. \label{eq:s1}
\end{eqnarray}
The definition of the kinematic factor $K$ is~\cite{Bel02b}\red{:}
\begin{equation}
K^2=\frac{t}{Q^2}\Big(1-\frac{t_{\textrm{min}}}{t}\Big)\Big(1-x_{\textrm{B}}\Big)\Big(1-y-\frac{y^2\epsilon^2}{4}\Big)\Big\lbrace\sqrt{1+\epsilon^2}+\frac{4x_{\textrm{B}}(1-x_{\textrm{B}})+\epsilon^2}{4(1-x_{\textrm{B}})}
\frac{t_{\textrm{min}}-t}{Q^2}\Big\rbrace\red{\,.}\label{eq:K}
\end{equation} 
The factor of $\Big(1-\frac{t_{\textrm{min}}}{t}\Big)$ implies that amplitudes proportional to these Fourier coefficients vanish as $-t$ approaches its minimum value.
The $\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$-function can be
written
\cite{Bel02b} 
\begin{equation}
 \mathcal{C}_{\textrm{unp}}^{\textrm{I}} = F_{1}\mathcal{H} + \frac{x_{\textrm{B}}}{2-x_{\textrm{B}}}(F_{1}+F_{2})\widetilde{\mathcal{H}} -\frac{t}{4M^{2}}F_{2}\mathcal{E},
\label{Eq_cunp}
\end{equation}
where $F_{1}$ and $F_{2}$ are respectively the Dirac and Pauli form
factors of the nucleon and $\mathcal{H}$, $\widetilde{\mathcal{H}}$ and
$\mathcal{E}$ are CFFs that relate respectively to the GPDs $H$,
$\widetilde{H}$ and $E$.  In H{\sc ermes} kinematic
conditions (where $x_{\textrm{B}}$ and $\frac{-t}{4M^2}$ are of order 0.1), the
contributions of CFFs $\widetilde{\mathcal{H}}$ and $\mathcal{E}$ can be
neglected in eq.~\ref{Eq_cunp} with respect to $\mathcal{H}$ (in first approximation) since they
are kinematically suppressed by an order of magnitude or more.
Hence, the behaviour of
$\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ is determined by CFF $\mathcal{H}$
and therefore GPD $H$ can be constrained through
measurements of the $\sin\phi$ and $\cos\phi$ terms of the $\mathcal{A}^{\textrm{I}}_{\textrm{LU}}(\phi)$ and $\mathcal{A}_{\textrm{C}}(\phi)$ asymmetries respectively.
